The Practical Application of MST

### 2021-02-21 article.Rmd
Use ggplot for ICC

```{r}
itemNo <- 5
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
plot(raschmodel, type = "ICC", items = itemNo, plot = TRUE, legend = TRUE)
```
This is the item characteristic curve (ICC), in this case for the fifth item in the trial data, `r itemID` with difficulty $b$ = `r itemDifficulty`.

>>>>

```{r}
itemNo <- 7
itemID <- str_extract(rownames(df_difficulties)[itemNo], "Item\\d+")
itemDifficulty <- df_difficulties[itemNo]
itemPlot <- data.frame(plot(raschmodel, type = "ICC", items = itemNo, plot = FALSE))
colnames(itemPlot) <- c('theta', 'probability')
ggplot(itemPlot, aes(x=theta, y=probability)) + 
  geom_line() +
  labs(title="Item Characteristic Curve", x="θ", y="P(X=1)")
```
This is the item characteristic curve (ICC), in this case for the seventh item in the trial data, `r itemID` with difficulty $b$ = `r itemDifficulty`.
